---
title: "XOR Neural Net Demo"
author: "Eddie Pantridge"
date: "Wednesday, February 10, 2016"
output: pdf_document
---

This is an example of how to create a simple neural network 
that will learn to comput XOR useing the neuralnet package.

First, lets get the library.
```{r}
library(neuralnet)
```

Next, lets create all the pattern for XOR.
```{r}
input_a <- c(0, 1, 0, 1)
input_b <- c(0, 0, 1, 1)
XORoutput  <- c(0, 1, 1, 0)
XORdata <- data.frame(input_a, input_b, XORoutput)

XORdata
```

We then must then   get the names of the input and output values from the datafram
```{r}
n <- names(XORdata)
n
```

Create, and train the neural network. Uses backpropagation.
Arguments:
- hidden = a vector of integers, each element gives the number of nodes in a hidden layer.
- linear.output = If TRUE, regression. If FALSE, classification.
- act.fct = Transfer function.
- stepmax = Max number of epochs to train.
```{r}
nn <- neuralnet(XORoutput~input_a+input_b, data=XORdata, hidden=c(3), linear.output=FALSE, act.fct="tanh", stepmax=1000)
```

The neuralnet package lets us make a plot of the network.
It shows the topoloy, bias and even weights!
```{r}
plot(nn)
```

Lets check each XOR pattern's output!
```{r}
compute(nn,XORdata[1:2])
```

